### 2023-01-19 doc/src/preface.tex
Make clear that the draft chapters won't change ratified parts
There were concerns that the draft chapters of this specification
might have an impact on the ratified parts once they advance.
Let's make it clear that this is not the case.

Signed-off-by: Christoph Müllner <christoph.muellner@vrull.eu>
Update version and preface for 1.0-RC2
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

>>>>

\section*{Changes for RC2 (Ratification Candidate 2)}

The only normative changes to this document
between versions RC1 and RC2 were to clarify that
field IID of CSR \z{hvictl} must support all
unsigned integer values of the number of bits implemented
for that field, and that writes to \z{hvictl}
always set IID in the most straightforward way.

A comment was added to Chapter~\ref{ch:IPIs} warning about
the possible need for FENCE instructions when IPIs are
sent to other harts by writing MSIs to those harts' IMSICs.
